---
title: 'EIE Survey 2020'
author: "admin"
output: pdf_document
---
## Inport the Google Sheet
```{r,echo=F, warning=F, message=F}
library(googlesheets4)
library(dplyr)
library(kableExtra)

form = read_sheet("https://docs.google.com/spreadsheets/d/1TVlhz1TQnMolJSlg8n_pnh0kW0qgnQEiiox3VKMp5AI/edit?usp=sharing")
```
## List of questions 

```{r,echo=F, warning=F, message=F}
form %>% select(-Horodateur) %>% colnames
```
### "3 words to describ the lab culture"

```{r,echo=F, warning=F, message=F}
R1 = form$`What 3 words would you use to describe our lab culture?`

library(SnowballC)
library(tm)

TextDoc <- Corpus(VectorSource(R1))

 #Replacing "/", "@" and "|" with space
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
your.stop.words = c()
TextDoc =  TextDoc %>%
  tm_map(., toSpace, "/") %>%
  tm_map(., toSpace, "@") %>%
  tm_map(., toSpace, "\\|") %>%
  # tm_map(., toSpace, ",") %>%
  # Convert the text to lower case
  tm_map(., content_transformer(tolower)) %>%
  # Remove numbers
  tm_map(., removeNumbers) %>%
  # Remove english common stopwords
  tm_map(., removeWords, stopwords("english")) %>%
  # Remove your own stop word
  tm_map(., removeWords, your.stop.words) %>%
  # Remove punctuations
  tm_map(., removePunctuation) %>%
  # Eliminate extra white spaces
  tm_map(., stripWhitespace)# %>%
  # Text stemming - which reduces words to their root form
  # tm_map(., stemDocument)

# Build a term-document matrix
TextDoc_dtm <- TermDocumentMatrix(TextDoc)
dtm_m <- as.matrix(TextDoc_dtm)
# Sort by descearing value of frequency
dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
# Display the top 5 most frequent words
# head(dtm_d, 5)

paste(sample(R1),collapse = ',')

library(wordcloud2)

wordcloud2(data = dtm_d)
```

### "What do you like most about working here?"

```{r,echo=F, warning=FALSE, message=FALSE}
R2 = form$`What do you like most about working here?`[!is.na(form$`What do you like most about working here?`)]

paste(sample(R2),collapse = '. ')
```

### "What do you like least about working here?"

```{r,echo=F, warning=FALSE, message=FALSE}
R3 = form$`What do you like least about working here?`[!is.na(form$`What do you like least about working here?`)]

paste(sample(R3),collapse = '. ')
```

### "How happy are you in the lab?"

```{r,echo=F, warning=FALSE, message=FALSE}
R4 = form$`How happy are you in the lab?`

library(ggplot2)

ggplot(data = form, aes(x = 1, y = `How happy are you in the lab?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_classic() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

### "Is there something that could be provided to make you happier?"

```{r,echo=F, warning=FALSE, message=FALSE}
R5 = form$`Is there something that could be provided to make you happier?`[!is.na(form$`Is there something that could be provided to make you happier?`)]

paste(sample(R5),collapse = '. ')
```

### "What is your impression of social life in the lab?"

```{r,echo=F, warning=FALSE, message=FALSE}
R6 = form$`What is your impression of social life in the lab?`

ggplot(data = form, aes(x = 1, y = `What is your impression of social life in the lab?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_classic() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) 
```

### "If you want to improve the social life in the lab, what are your suggestions for achieving this?"

```{r,echo=F, warning=FALSE, message=FALSE}
R7 = form$`If you want to improve the social life in the lab, what are your suggestions for achieving this?`[!is.na(form$`If you want to improve the social life in the lab, what are your suggestions for achieving this?`)]

paste(sample(R7),collapse = '. ')
```

### "How comfortable do you feel sharing personal concerns (housing, financial, family, physical or mental health) with Nico?"

```{r,echo=F, warning=FALSE, message=FALSE}
R8 = form$`How comfortable do you feel sharing personal concerns (housing, financial, family, physical or mental health) with Nico?`

ggplot(data = form, aes(x = 1, y = `How comfortable do you feel sharing personal concerns (housing, financial, family, physical or mental health) with Nico?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) 
```

### Pressure

```{r,echo=F, warning=FALSE, message=FALSE}
R9 = form$`Do you feel explicit or implicit pressure to work more hours than you feel is healthy?`

R10 = form$`Do you feel explicit or implicit pressure to publish?`

R11 = form$`Do you feel explicit or implicit pressure to avoid taking vacations?`

R12 = form$`If you feel pressured, does this pressure have negative effects on you well being and productivity?`

ggpubr::ggarrange(
  ggplot(data = form, aes(x = 1, y = `Do you feel explicit or implicit pressure to work more hours than you feel is healthy?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  labs(y = 'Do you feel explicit or implicit pressure to work \n more hours than you feel is healthy?') +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  
  ggplot(data = form, aes(x = 1, y = `Do you feel explicit or implicit pressure to publish?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10))+ 
  labs(y = 'Do you feel explicit or implicit pressure\nto publish?') +
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  
  ggplot(data = form, aes(x = 1, y = `Do you feel explicit or implicit pressure to avoid taking vacations?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  labs(y = 'Do you feel explicit or implicit pressure\nto avoid taking vacations?') +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
    ggplot(data = form, aes(x = 1, y = `If you feel pressured, does this pressure have negative effects on you well being and productivity?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  labs(y = 'If you feel pressured, does this pressure \nhave negative effects on you well being and productivity?') +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  ncol = 4
)
 
```

```{r,echo=F, warning=FALSE, message=FALSE}
R13 = form$`What can we do to reduce these pressures?`[!is.na(form$`What can we do to reduce these pressures?`)]

paste(sample(R13),collapse = '. ')
```

### Harassment

```{r,echo=F, warning=FALSE, message=FALSE}
R14 = form$`Have you experienced or witnessed a hostile work environment in the lab? (bullying, gender harassment, sexual harassment)`

    ggplot(data = form, aes(x = 1, y = `Have you experienced or witnessed a hostile work environment in the lab? (bullying, gender harassment, sexual harassment)`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

### Communication

#### "How well does the lab communicate as a whole?"

```{r,echo=F, warning=FALSE, message=FALSE}
R15 = form$`How well does the lab communicate as a whole?`

    ggplot(data = form, aes(x = 1, y = `How well does the lab communicate as a whole?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "What are some ways that we could improve communication in the lab?"

```{r,echo=F, warning=FALSE, message=FALSE}
R16 = form$`What are some ways that we could improve communication in the lab?`[!is.na(form$`What are some ways that we could improve communication in the lab?`)]

paste(sample(R16),collapse = '. ')
```

### Lab rules

#### "Do you feel that lab rules/policies are clear? Are there unspoken rules or policies that you feel should be more clearly communicated?"

```{r,echo=F, warning=FALSE, message=FALSE}
R17 = form$`Do you feel that lab rules/policies are clear? Are there unspoken rules or policies that you feel should be more clearly communicated?`[!is.na(form$`Do you feel that lab rules/policies are clear? Are there unspoken rules or policies that you feel should be more clearly communicated?`)]

paste(sample(R17),collapse = '. ')
```

#### "Are there policies you feel should be explicitly written? If so, please explain which ones."

```{r,echo=F, warning=FALSE, message=FALSE}
R18 = form$`Are there policies you feel should be explicitly written? If so, please explain which ones.`[!is.na(form$`Are there policies you feel should be explicitly written? If so, please explain which ones.`)]

paste(sample(R18),collapse = '. ')
```
#### "Do you feel that the same rules apply to everyone in lab? If not, please explain."

```{r,echo=F, warning=FALSE, message=FALSE}
R19 = form$`Do you feel that the same rules apply to everyone in lab? If not, please explain.`[!is.na(form$`Do you feel that the same rules apply to everyone in lab? If not, please explain.`)]

paste(sample(R19),collapse = '. ')
```
### Empowerement

#### "Do you feel empowered to make suggestions to Nico to improve the lab culture/ organization?"

```{r,echo=F, warning=FALSE, message=FALSE}
R20 = form$`Do you feel empowered to make suggestions to Nico to improve the lab culture/ organization?` %>% factor

summary(R20)
```

#### "Do you feel empowered to make suggestions to Nico to improve the lab culture/ organization?"

```{r,echo=F, warning=FALSE, message=FALSE}
R21 = form$`Do you feel empowered to make suggestions to your colleagues to improve the lab culture/ organization?` %>% factor

summary(R21)
```
#### "If you do not feel empowered to make suggestions to your colleagues in the lab or to Nico to improve the lab culture/ organization, please tell me more about this."

```{r,echo=F, warning=FALSE, message=FALSE}
R22 = form$`If you do not feel empowered to make suggestions to your colleagues in the lab or to Nico to improve the lab culture/ organization, please tell me more about this.`[!is.na(form$`If you do not feel empowered to make suggestions to your colleagues in the lab or to Nico to improve the lab culture/ organization, please tell me more about this.`)]

paste(sample(R22),collapse = '. ')
```
### Supervision 

```{r,echo=F, warning=FALSE, message=FALSE}
R23 = form$`Do you feel you have enough feedback on your project?`
R24 = form$`Do you feel you have enough time to meet with Nico?`
R25 = form$`How useful do you find one-on-one meetings with Nico?`

ggpubr::ggarrange(
  ggplot(data = form, aes(x = 1, y = `Do you feel you have enough feedback on your project?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  labs(y = 'Do you feel you have enough feedback on your project?') +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  
  ggplot(data = form, aes(x = 1, y = `Do you feel you have enough time to meet with Nico?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10))+ 
  labs(y = 'Do you feel you have enough time to meet with Nico?') +
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  
  ggplot(data = form, aes(x = 1, y = `How useful do you find one-on-one meetings with Nico?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  labs(y = 'How useful do you find one-on-one meetings with Nico?') +
  lims(y = c(0,10))+ 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  ncol = 3
)
 
```

#### "Is there something that could make these meetings more useful or productive?"

```{r,echo=F, warning=FALSE, message=FALSE}
R26 = form$`Is there something that could make these meetings more useful or productive?`[!is.na(form$`Is there something that could make these meetings more useful or productive?`)]

paste(sample(R26),collapse = '. ')
```

#### "Do you think the current system of scheduling one-on-one meetings is working?  Should these be less frequent, more frequent, or stay as is?"

```{r,echo=F, warning=FALSE, message=FALSE}
R27 = form$`Do you think the current system of scheduling one-on-one meetings is working?  Should these be less frequent, more frequent, or stay as is?`[!is.na(form$`Do you think the current system of scheduling one-on-one meetings is working?  Should these be less frequent, more frequent, or stay as is?`)]

paste(sample(R27),collapse = '. ')
```

#### "Do you think you would benefit from more formal feedback on your progress?"

```{r,echo=F, warning=FALSE, message=FALSE}
R28 = form$`Do you think you would benefit from more formal feedback on your progress?` [!is.na(form$`Do you think you would benefit from more formal feedback on your progress?`)]

paste(sample(R28),collapse = '. ')
```

#### "How supported do you feel by Nico, and do you think that you are getting the mentoring, career advice, and general guidance to succeed?"

```{r,echo=F, warning=FALSE, message=FALSE}
R29 = form$`How supported do you feel by Nico, and do you think that you are getting the mentoring, career advice, and general guidance to succeed?`

ggplot(data = form, aes(x = 1, y = `How supported do you feel by Nico, and do you think that you are getting the mentoring, career advice, and general guidance to succeed?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "Do you want formal training in giving talks?"

```{r,echo=F, warning=FALSE, message=FALSE}
R30 = form$`Do you want formal training in giving talks?` %>% factor

summary(R30)
```

#### "Do you want to have more than an Annual Mentoring Meeting to go over your Individual Development Plan and discuss post-PhD or post-Postdoc plans?"

```{r,echo=F, warning=FALSE, message=FALSE}
R31 = form$`Do you want to have more than an Annual Mentoring Meeting to go over your Individual Development Plan and discuss post-PhD or post-Postdoc plans?` %>% factor

summary(R31)
```

#### "What kind of advice or information would be useful to discuss at such an Annual Mentoring Meeting?"

```{r,echo=F, warning=FALSE, message=FALSE}
R32 = form$`What kind of advice or information would be useful to discuss at such an Annual Mentoring Meeting?` [!is.na(form$`What kind of advice or information would be useful to discuss at such an Annual Mentoring Meeting?`)]

paste(sample(R32),collapse = '. ')
```

#### "Do you have any explicit feedback on how Nico can improve his mentoring style?"

```{r,echo=F, warning=FALSE, message=FALSE}
R33 = form$`Do you have any explicit feedback on how Nico can improve his mentoring style?`[!is.na(form$`Do you have any explicit feedback on how Nico can improve his mentoring style?`)]

paste(sample(R33),collapse = '. ')
```

```{r,echo=F, warning=FALSE, message=FALSE}
R34 = form$`Do you feel it is easy to get information from Nico?`
R35 = form$`Do you feel it is easy to get information from other people in the lab?`

ggpubr::ggarrange(
  ggplot(data = form, aes(x = 1, y = `Do you feel it is easy to get information from Nico?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) +
  labs(y = "Do you feel it is easy to get information from Nico?") +
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()),
  ggplot(data = form, aes(x = 1, y = `Do you feel it is easy to get information from other people in the lab?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) +
  labs(y = "Do you feel it is easy to get information\nfrom other people in the lab?") +
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()), 
  ncol = 2
)
```

### Meetings

#### "How useful do you find lab meetings?"

```{r,echo=F, warning=FALSE, message=FALSE}
R36 = form$`How useful do you find lab meetings?`

ggplot(data = form, aes(x = 1, y = `How useful do you find lab meetings?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "Is there something that could make project-based meetings more useful or productive?"

```{r,echo=F, warning=FALSE, message=FALSE}
R37 = form$`Is there something that could make project-based meetings more useful or productive?`[!is.na(form$`Is there something that could make project-based meetings more useful or productive?`)]

paste(sample(R37),collapse = '. ')
```

#### "How useful do you find the 46sec journal club?"

```{r,echo=F, warning=FALSE, message=FALSE}
R38 = form$`How useful do you find the 46sec journal club?`

ggplot(data = form, aes(x = 1, y = `How useful do you find the 46sec journal club?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "Is there something that could make the journal club more useful or productive?"

```{r,echo=F, warning=FALSE, message=FALSE}
R39 = form$`Is there something that could make the journal club more useful or productive?`[!is.na(form$`Is there something that could make the journal club more useful or productive?`)]

paste(sample(R39),collapse = '. ')
```

### Work 

#### "How much freedom do you feel you have to decide how you do your work?"

```{r,echo=F, warning=FALSE, message=FALSE}
R40 = form$`How much freedom do you feel you have to decide how you do your work?`

ggplot(data = form, aes(x = 1, y = `How much freedom do you feel you have to decide how you do your work?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "How collaborative do you think the lab is?"

```{r,echo=F, warning=FALSE, message=FALSE}
R41 = form$`How collaborative do you think the lab is?`

ggplot(data = form, aes(x = 1, y = `How collaborative do you think the lab is?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

#### "Do you perceive that there is any favoritism in the lab? Please elaborate"

```{r,echo=F, warning=FALSE, message=FALSE}
R42 = form$`Do you perceive that there is any favoritism in the lab? Please elaborate.`[!is.na(form$`Do you perceive that there is any favoritism in the lab? Please elaborate.`)]

paste(sample(R42),collapse = '. ')
```

#### "Are there any issues with collaborations in the lab that are not working? Please explain."

```{r,echo=F, warning=FALSE, message=FALSE}
R43 = form$`Are there any issues with collaborations in the lab that are not working? Please explain.`[!is.na(form$`Are there any issues with collaborations in the lab that are not working? Please explain.`)]

paste(sample(R43),collapse = '. ')
```

#### "Are you aware of the lab's authorship policies?"

```{r,echo=F, warning=FALSE, message=FALSE}
R44 = form$`Are you aware of the lab's authorship policies?` %>% factor

summary(R44)
```

#### "Do have any concerns about anticipated authorship on papers describing your work or collaborations that you are involved with?"

```{r,echo=F, warning=FALSE, message=FALSE}
R45 = form$`Do have any concerns about anticipated authorship on papers describing your work or collaborations that you are involved with?`[!is.na(form$`Do have any concerns about anticipated authorship on papers describing your work or collaborations that you are involved with?`)]

paste(sample(R45),collapse = '. ')
```

#### "Please rate whether you feel the lab provides you with the tools and technologies you need?"

```{r,echo=F, warning=FALSE, message=FALSE}
R46 = form$`Please rate whether you feel the lab provides you with the tools and technologies you need?`

ggplot(data = form, aes(x = 1, y = `Please rate whether you feel the lab provides you with the tools and technologies you need?`)) + 
  geom_violin(fill = 'gray') +
  geom_boxplot(width = .5) + 
  geom_jitter(width = .1) +
  lims(y = c(0,10)) + 
  theme_bw() + 
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```
